*Prochlorococcus marinus* responses to light and oxygen

### 2024-06-06 Code/Manuscript_O2.Rmd
minor text edit to map discussion

Expansion of OMZ would drastically alter these patterns of potential niche extensions, by allowing clade LLIV to exploit a much wider range of lights, extending towards near-surface niches in both tropical and temperate zones, under permissive temperatures.

>>>>

Expansion of OMZ would drastically alter these patterns of potential niche extensions, by further restricting occurrences of clade HLI, but allowing clade LLIV to exploit a much wider range of lights, extending towards near-surface niches in both tropical and temperate zones, under permissive temperatures.
